---
title: "chp5"
author: "George Oberle"
date: "May 2, 2015"
output: html_document
---

```{r}
library (sp)
library (rgdal)
library (rgeos)
library (maptools)
library (ggmap)
library (ggplot2)
library (mullenMisc)
library (magrittr)
library (stringr)
library (dplyr)
library (RColorBrewer)
library (igraph)

```


```{r}
early_learned <- read.csv("~/chp5/data/schol-soc-geocoded.csv")
silliman_societies <- read.csv("~/chp5/data/Scientific_Societies_1825_American_Journal_of_Science_and_Arts.csv")
bates_early_learned <-read.csv("~/chp5/data/Early Learned Societies Bates 2.csv")
scilearn <- read.csv ("~/chp5/data/scilearned.csv")
libraries <- read.csv("~/chp5/data/libraries.csv")
dclibraries<- read.csv ("~/chp5/data/dclibrariesmod.csv")
militacad<- read.csv ("~/chp5/data/Military_Education_Military_Academy_List.csv")
```


```{r}
#Maps Begin
militacad %>%
   mutate (location=paste (City,State))
militacad
```
#This is not working
location_geocoded <- geocode(militacad$location)
militacad_geocoded <- cbind(militacad, location_geocoded)

militacad_geocoded
write.csv(schol_soc_geocoded, file = "schol-soc-geocoded.csv")


location_geocoded <- geocode(militacad$location)
militacad_geocoded <- cbind(militacad, location_geocoded)
militacad_geocoded



#Maps-Scholarly Societies Begin
schol_soc <- read.csv("~/societiesnetwork/data/scholarlysocieties.csv")     
schol_soc<- schol_soc%>%
mutate(location=paste (City, State))
location_geocoded <- geocode(schol_soc$location)
schol_soc_geocoded <- cbind(schol_soc, location_geocoded)
schol_soc_geocoded
write.csv(schol_soc_geocoded, file = "schol-soc-geocoded.csv")

```{r}
dclibraries %>%

  round_year(set_of_years) # round to decade by default
  
  
  mutate(location=paste (City, State))
location_geocoded <- geocode(schol_soc$location)
schol_soc_geocoded <- cbind(schol_soc, location_geocoded)
schol_soc_geocoded



dclib <- ggplot(dclibraries, aes (x=Founding.Date, fill=Type))
dclib+ geom_histogram(position= "stack", binwidth= 10) + theme(axis.text.x = element_text(face = "bold", angle = 60, hjust = 1, size = 8)) +ggtitle("Learned Societies by Date Established") + ylab("Total Established") + xlab ("Year Established")

```

```{r}

dclib <-ggplot(dclibraries, aes (x=Founding.Date, Fill=Types))
geom_histogram(dclib, + ggtitle("Learned Societies Established 1768-1848") + ylab("Total Established")




```



